Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-07-17 aosd13/pepm13/caseStudyDiscussion.tex
Use ~ after Ch./Sec./Ch/Sec in citations
And add missing dots.

As a consequence, to the best of our knowledge some properties of type inference have not been formally established.
For instance, a reasonable user expectation is that removing a call to an implicit conversion does not alter the program, if it is the only implicit conversion with the correct type in scope, or if it is more specific than the others~\citep[Ch. 21]{Odersky11book}. This is not always correct, because removing the implicit conversion reduces the information available for the type inference algorithm; we observed multiple cases\footnote{\url{https://issues.scala-lang.org/browse/SI-5592}, reported by us.} where type inference becomes unable to figure out enough information about the type to trigger implicit conversion.

We also consider significant that Scala 2.8 required making both type inference and implicit resolution more powerful, specifically in order to support the collection library~\citep[Sec 21.7]{Moors10TCP,Odersky11book}; further extensions would be possible and desirable.
For instance, if type inference were extended with higher-order unification\footnote{\url{https://issues.scala-lang.org/browse/SI-2712}}~\citep{Pfenning88}, it would better support a part of our DSL interface (not discussed in this chapter) by removing the need for type annotations.
%\pg{That's type indexing, to describe earlier}.

>>>>

As a consequence, to the best of our knowledge some properties of type inference have not been formally established.
For instance, a reasonable user expectation is that removing a call to an implicit conversion does not alter the program, if it is the only implicit conversion with the correct type in scope, or if it is more specific than the others~\citep[Ch.~21]{Odersky11book}. This is not always correct, because removing the implicit conversion reduces the information available for the type inference algorithm; we observed multiple cases\footnote{\url{https://issues.scala-lang.org/browse/SI-5592}, reported by us.} where type inference becomes unable to figure out enough information about the type to trigger implicit conversion.

We also consider significant that Scala 2.8 required making both type inference and implicit resolution more powerful, specifically in order to support the collection library~\citep[Sec.~21.7]{Moors10TCP,Odersky11book}; further extensions would be possible and desirable.
For instance, if type inference were extended with higher-order unification\footnote{\url{https://issues.scala-lang.org/browse/SI-2712}}~\citep{Pfenning88}, it would better support a part of our DSL interface (not discussed in this chapter) by removing the need for type annotations.
%\pg{That's type indexing, to describe earlier}.
